---
title: "reprex"
author: "Allison Horst"
date: "8/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
```

Your job is to identify an error, then make a reproducible example that would help future you or someone else understand how to write the code correctly. In other words, your reprex code will *work* and offer a solution to the error thrown in each of the following examples.

Data are in `AS00601.csv` (and read in correctly below as `mack_creek_vertebrates`).

Data package title: Aquatic Vertebrate Population Study in Mack Creek, Andrews Experimental Forest, 1987 to present

**Citation:** Gregory, S.V. and I. Arismendi. 2020. Aquatic Vertebrate Population Study in Mack Creek, Andrews Experimental Forest, 1987 to present ver 14. Environmental Data Initiative. <https://doi.org/10.6073/pasta/7c78d662e847cdbe33584add8f809165>

### Read in the data

There are no problems here.

```{r}
mack_creek_vertebrates <- read_csv(here("AS00601.csv"))
```

### reprex 1

Identify what is causing the problem in the code below (there's only one thing). Then, create a very simple reprex that would help yourself, future you, or a colleague fix the problem. **Post your reprex as an issue in your own fork on GitHub.**

```{r}
# Example 1: 
mack_creek_lengths <- mack_creek_vertebrates %>% 
  clean_names() %>% 
  select(year:sampledate) %>% 
  filter(section == "CC") %>% 
  mutate(across(where(is.character, tolower))) %>% 
  drop_na(species) %>% 
  group_by(species) %>% 
  summarize(mean_length_cm = mean(length1, na.rm = TRUE),
            sd_length_cm = sd(length1, na.rm = TRUE)) %>% 
  ungroup()

```

```{r}
# create new subset of dataframe for issue
library(tidyverse)
library(janitor)
mack_creek_lengths_subset <- mack_creek_vertebrates %>% 
  clean_names() %>% 
  select(year:sampledate) %>% 
  filter(section == "CC") %>%
  slice_head(n = 10)

datapasta::df_paste(mack_creek_lengths_subset)


mack_creek_lengths_subset <-  data.frame(
  stringsAsFactors = FALSE,
                                            year = c(1987,1987,1987,1987,
                                                     1987,1987,1987,1987,1987,
                                                     1987),
                                        sitecode = c("MACKCC-L","MACKCC-L",
                                                     "MACKCC-L","MACKCC-L",
                                                     "MACKCC-L","MACKCC-L",
                                                     "MACKCC-L","MACKCC-L","MACKCC-L",
                                                     "MACKCC-L"),
                                         section = c("CC","CC","CC","CC",
                                                     "CC","CC","CC","CC","CC",
                                                     "CC"),
                                           reach = c("L","L","L","L","L",
                                                     "L","L","L","L","L"),
                                            pass = c(1,1,1,1,1,1,1,1,1,
                                                     1),
                                         unitnum = c(1,1,1,1,1,1,1,1,1,
                                                     1),
                                        unittype = c("R","R","R","R","R",
                                                     "R","R","R","R","R"),
                                      vert_index = c(1,2,3,4,5,6,7,8,9,
                                                     10),
                                       pitnumber = c(NA,NA,NA,NA,NA,NA,
                                                     NA,NA,NA,NA),
                                         species = c("ONCL","ONCL","ONCL",
                                                     "ONCL","ONCL","ONCL",
                                                     "ONCL","ONCL","ONCL","ONCL"),
                                         length1 = c(58,61,89,58,93,86,
                                                     107,131,103,117),
                                         length2 = c(NA,NA,NA,NA,NA,NA,
                                                     NA,NA,NA,NA),
                                          weight = c(1.75,1.95,5.6,2.15,
                                                     6.9,5.9,10.5,20.6,9.55,
                                                     13),
                                            clip = c("NONE","NONE","NONE",
                                                     "NONE","NONE","NONE",
                                                     "NONE","NONE","NONE","NONE"),
                                      sampledate = c("10/7/87","10/7/87",
                                                     "10/7/87","10/7/87",
                                                     "10/7/87","10/7/87","10/7/87",
                                                     "10/7/87","10/7/87",
                                                     "10/7/87")
                              )

mack_creek_lengths_subset %>%
  mutate(across(where(is.character, tolower))) %>%
  drop_na(species) %>%
  group_by(species) %>%
  summarize(mean_length_cm = mean(length1, na.rm = TRUE),
            sd_length_cm = sd(length1, na.rm = TRUE)) %>%
  ungroup()

```

reprex output here:

```{r}
library(tidyverse)
library(janitor)
#> 
#> Attaching package: 'janitor'
#> The following objects are masked from 'package:stats':
#> 
#>     chisq.test, fisher.test
mack_creek_lengths_subset <- mack_creek_vertebrates %>% 
  clean_names() %>% 
  select(year:sampledate) %>% 
  filter(section == "CC") %>%
  slice_head(n = 10)
#> Error: object 'mack_creek_vertebrates' not found

datapasta::df_paste(mack_creek_lengths_subset)
#> Error: object 'mack_creek_lengths_subset' not found


mack_creek_lengths_subset <-  data.frame(
  stringsAsFactors = FALSE,
                                            year = c(1987,1987,1987,1987,
                                                     1987,1987,1987,1987,1987,
                                                     1987),
                                        sitecode = c("MACKCC-L","MACKCC-L",
                                                     "MACKCC-L","MACKCC-L",
                                                     "MACKCC-L","MACKCC-L",
                                                     "MACKCC-L","MACKCC-L","MACKCC-L",
                                                     "MACKCC-L"),
                                         section = c("CC","CC","CC","CC",
                                                     "CC","CC","CC","CC","CC",
                                                     "CC"),
                                           reach = c("L","L","L","L","L",
                                                     "L","L","L","L","L"),
                                            pass = c(1,1,1,1,1,1,1,1,1,
                                                     1),
                                         unitnum = c(1,1,1,1,1,1,1,1,1,
                                                     1),
                                        unittype = c("R","R","R","R","R",
                                                     "R","R","R","R","R"),
                                      vert_index = c(1,2,3,4,5,6,7,8,9,
                                                     10),
                                       pitnumber = c(NA,NA,NA,NA,NA,NA,
                                                     NA,NA,NA,NA),
                                         species = c("ONCL","ONCL","ONCL",
                                                     "ONCL","ONCL","ONCL",
                                                     "ONCL","ONCL","ONCL","ONCL"),
                                         length1 = c(58,61,89,58,93,86,
                                                     107,131,103,117),
                                         length2 = c(NA,NA,NA,NA,NA,NA,
                                                     NA,NA,NA,NA),
                                          weight = c(1.75,1.95,5.6,2.15,
                                                     6.9,5.9,10.5,20.6,9.55,
                                                     13),
                                            clip = c("NONE","NONE","NONE",
                                                     "NONE","NONE","NONE",
                                                     "NONE","NONE","NONE","NONE"),
                                      sampledate = c("10/7/87","10/7/87",
                                                     "10/7/87","10/7/87",
                                                     "10/7/87","10/7/87","10/7/87",
                                                     "10/7/87","10/7/87",
                                                     "10/7/87")
                              )

mack_creek_lengths_subset %>%
  mutate(across(where(is.character, tolower))) %>%
  drop_na(species) %>%
  group_by(species) %>%
  summarize(mean_length_cm = mean(length1, na.rm = TRUE),
            sd_length_cm = sd(length1, na.rm = TRUE)) %>%
  ungroup()
#> Error in `mutate()`:
#> ℹ In argument: `across(where(is.character, tolower))`.
#> Caused by error in `across()`:
#> ℹ In argument: `where(is.character, tolower)`.
#> Caused by error in `where()`:
#> ! unused argument (tolower)
```


### reprex 2

Identify what is causing the problem in the code below (there's only one thing). Then, create a very simple reprex that would help yourself, future you, or a colleague fix the problem. **Post your reprex as an issue in your own fork on GitHub.**

```{r}
# Example 2:
mack_creek_vertebrates %>% 
  clean_names() %>% 
  filter(species == "ONCL") %>% 
  ggplot(aes(x = length1, y = weight)) +
         geom_point(aes(shape = 12), color = "purple") +
         theme_minimal() +
         labs(x = "Cutthroat trout length (cm)",
              y = "Weight (g)")

```

```{r}
#_________________________
library(tidyverse)
library(janitor)

mack_creek_vertebrates_subset <-  mack_creek_vertebrates %>% 
  clean_names() %>% 
  filter(species == "ONCL") %>% slice_head(n = 10)

datapasta::df_paste(mack_creek_vertebrates_subset)



mack_creek_vertebrates_subset <-  data.frame(
  stringsAsFactors = FALSE,
                                              dbcode = c("AS006",
                                                         "AS006","AS006",
                                                         "AS006","AS006","AS006",
                                                         "AS006","AS006",
                                                         "AS006","AS006"),
                                              entity = c(1,1,1,
                                                         1,1,1,1,1,1,1),
                                                year = c(1987,
                                                         1987,1987,1987,1987,
                                                         1987,1987,1987,1987,
                                                         1987),
                                            sitecode = c("MACKCC-L","MACKCC-L",
                                                         "MACKCC-L","MACKCC-L",
                                                         "MACKCC-L","MACKCC-L",
                                                         "MACKCC-L","MACKCC-L",
                                                         "MACKCC-L","MACKCC-L"),
                                             section = c("CC",
                                                         "CC","CC","CC","CC",
                                                         "CC","CC","CC","CC",
                                                         "CC"),
                                               reach = c("L","L",
                                                         "L","L","L","L",
                                                         "L","L","L","L"),
                                                pass = c(1,1,1,
                                                         1,1,1,1,1,1,1),
                                             unitnum = c(1,1,1,
                                                         1,1,1,1,1,1,1),
                                            unittype = c("R","R",
                                                         "R","R","R","R",
                                                         "R","R","R","R"),
                                          vert_index = c(1,2,3,
                                                         4,5,6,7,8,9,10),
                                           pitnumber = c(NA,NA,
                                                         NA,NA,NA,NA,NA,NA,
                                                         NA,NA),
                                             species = c("ONCL",
                                                         "ONCL","ONCL","ONCL",
                                                         "ONCL","ONCL","ONCL",
                                                         "ONCL","ONCL","ONCL"),
                                             length1 = c(58,61,
                                                         89,58,93,86,107,131,
                                                         103,117),
                                             length2 = c(NA,NA,
                                                         NA,NA,NA,NA,NA,NA,
                                                         NA,NA),
                                              weight = c(1.75,
                                                         1.95,5.6,2.15,6.9,5.9,
                                                         10.5,20.6,9.55,13),
                                                clip = c("NONE",
                                                         "NONE","NONE","NONE",
                                                         "NONE","NONE","NONE",
                                                         "NONE","NONE","NONE"),
                                          sampledate = c("10/7/87",
                                                         "10/7/87","10/7/87",
                                                         "10/7/87","10/7/87",
                                                         "10/7/87","10/7/87",
                                                         "10/7/87","10/7/87",
                                                         "10/7/87"),
                                               notes = c(NA,NA,
                                                         NA,NA,NA,NA,NA,NA,
                                                         NA,NA)
                                  )


mack_creek_vertebrates_subset %>% ggplot(aes(x = length1, y = weight)) +
         geom_point(aes(shape = 12), color = "purple") +
         theme_minimal() +
         labs(x = "Cutthroat trout length (cm)",
              y = "Weight (g)")
```

#### second reprex here:

```{r}
library(tidyverse)
library(janitor)
#> 
#> Attaching package: 'janitor'
#> The following objects are masked from 'package:stats':
#> 
#>     chisq.test, fisher.test

mack_creek_vertebrates_subset <-  mack_creek_vertebrates %>% 
  clean_names() %>% 
  filter(species == "ONCL") %>% slice_head(n = 10)
#> Error: object 'mack_creek_vertebrates' not found

datapasta::df_paste(mack_creek_vertebrates_subset)
#> Error: object 'mack_creek_vertebrates_subset' not found



mack_creek_vertebrates_subset <-  data.frame(
  stringsAsFactors = FALSE,
                                              dbcode = c("AS006",
                                                         "AS006","AS006",
                                                         "AS006","AS006","AS006",
                                                         "AS006","AS006",
                                                         "AS006","AS006"),
                                              entity = c(1,1,1,
                                                         1,1,1,1,1,1,1),
                                                year = c(1987,
                                                         1987,1987,1987,1987,
                                                         1987,1987,1987,1987,
                                                         1987),
                                            sitecode = c("MACKCC-L","MACKCC-L",
                                                         "MACKCC-L","MACKCC-L",
                                                         "MACKCC-L","MACKCC-L",
                                                         "MACKCC-L","MACKCC-L",
                                                         "MACKCC-L","MACKCC-L"),
                                             section = c("CC",
                                                         "CC","CC","CC","CC",
                                                         "CC","CC","CC","CC",
                                                         "CC"),
                                               reach = c("L","L",
                                                         "L","L","L","L",
                                                         "L","L","L","L"),
                                                pass = c(1,1,1,
                                                         1,1,1,1,1,1,1),
                                             unitnum = c(1,1,1,
                                                         1,1,1,1,1,1,1),
                                            unittype = c("R","R",
                                                         "R","R","R","R",
                                                         "R","R","R","R"),
                                          vert_index = c(1,2,3,
                                                         4,5,6,7,8,9,10),
                                           pitnumber = c(NA,NA,
                                                         NA,NA,NA,NA,NA,NA,
                                                         NA,NA),
                                             species = c("ONCL",
                                                         "ONCL","ONCL","ONCL",
                                                         "ONCL","ONCL","ONCL",
                                                         "ONCL","ONCL","ONCL"),
                                             length1 = c(58,61,
                                                         89,58,93,86,107,131,
                                                         103,117),
                                             length2 = c(NA,NA,
                                                         NA,NA,NA,NA,NA,NA,
                                                         NA,NA),
                                              weight = c(1.75,
                                                         1.95,5.6,2.15,6.9,5.9,
                                                         10.5,20.6,9.55,13),
                                                clip = c("NONE",
                                                         "NONE","NONE","NONE",
                                                         "NONE","NONE","NONE",
                                                         "NONE","NONE","NONE"),
                                          sampledate = c("10/7/87",
                                                         "10/7/87","10/7/87",
                                                         "10/7/87","10/7/87",
                                                         "10/7/87","10/7/87",
                                                         "10/7/87","10/7/87",
                                                         "10/7/87"),
                                               notes = c(NA,NA,
                                                         NA,NA,NA,NA,NA,NA,
                                                         NA,NA)
                                  )


mack_creek_vertebrates_subset %>% ggplot(aes(x = length1, y = weight)) +
         geom_point(aes(shape = 12), color = "purple") +
         theme_minimal() +
         labs(x = "Cutthroat trout length (cm)",
              y = "Weight (g)")
#> Error in `geom_point()`:
#> ! Problem while computing aesthetics.
#> ℹ Error occurred in the 1st layer.
#> Caused by error in `scale_f()`:
#> ! A continuous variable cannot be mapped to the shape aesthetic.
#> ℹ Choose a different aesthetic or use `scale_shape_binned()`.
```

<sup>Created on 2025-08-21 with [reprex v2.1.1](https://reprex.tidyverse.org)</sup> \`\`\`

## End
